---
title: "Developing Data Products Course Project"
author: "Jean-Marc Terrettaz"
date: "10/13/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description

This small app shows the number of air passengers per month in the years 1949-1960. 

The number of passengers are taken from R's dataset AirPassengers. 

## How to use the app

- Select the year in the input box on the left side
- The number of air passergers for this year are shown in the plot on the right side.

## Example: Air Passengers for year 1951

The following code draws the plot for year 1951:
```{r echo = TRUE, out.height=200, out.width=400}
year <- 1951
df <- data.frame(AirPassengers, year = trunc(time(AirPassengers)), 
   month = month.abb[cycle(AirPassengers)])
selected <- df[df$year==year,c(3,1)]
plot_title <- paste('Air passengers for year',year )
barplot(height = as.vector(selected$AirPassengers), 
        names.arg = selected$month,  main = plot_title)
```

## Code

The code is available at: https://github.com/jmterrettaz/DataProducts/tree/master/CourseProject

Enjoy!